%%%%%

\documentclass[char]{guildcamp1}
\begin{document}

\name{\cCaptain{}}

\cenquote{``I have slipped the surly bonds of earth,\\And danced the skies on laughter-silvered wings.''}{-- John Magee}

You always joked that you had two daughters, and could never decide
which was the lovelier. The first, of course, is the {\it HMS
Dauntless}, finest ship is Her Majesty's aerial navy. She boasts a
groundbreaking design, a flawless construction, a talented crew, and a
fine captain. Back in the Steam War, you flew smaller, lighter, slower
craft. A wood and metal chassis really, with a noisy steam engine
strapped to the back, and a daredevil pilot in front with nothing but
an artillery piece and his training for survival in the brutal
skies. You don't dwell on it too long. The Steam War is something you
have mixed feelings on. On the one hand, for mere hours a day you
could escape the low earth, and soar among the clouds. On the other
hand, war is hell. It's not an experience you would wish on your worst
enemies. Not even on your former wife. Still, you and your wingman,
Lord Cornelius Blackwell, survived somehow, found a little bit of
glory up in the skies, and made a lasting and deep friendship.

So you love the {\it HMS Dauntless} as if it were a child. And it is,
to some extent. You conceived of its revolutionary design, found the
creditors to finance the project, and brought this dream to life. The
ship grew much as your other daughter did, dreamed up by you just a
few weeks after she was born on a rainy day just over eighteen years
ago{\ldots}. The project was a small one at first, and the first few
years were quite stormy. Mary was a rambunctious little girl, always
getting herself into one form of trouble or another, usually involving
her refusal to respect other people's posessions. You remember fondly,
and often retell at dinner parties, a certain comical incident at a
candy store. This must have been in '76, when Mary was but five years
old. You let her wander around freely while you bought some crushed
licorice for an upcoming party. When the two of you turned to leave
the store, a single caramel dropped from the inside of Mary's
dress. As she reached down to pick it up, a literal torrent of sweets
exploded from her clothing, covering the ground. She had a dozen
pounds' worth of cheap sugar, all hidden away in her clothing. You
tease her about that every once in a while, in a warm fatherly way,
and you and Cornelius have had many laughs about that.

{\it She's still yours.} Every day you thank God that Mary is. And the
{\it Dauntless} as well. See, your ex-wife (this is how you like to
refer to her in polite company), \cCurie{\intro}, wanted to take both
of your daughters away. You can't even remember why in the nine
circles of Hell you married that woman. That controlling, arrogant,
sadistic harpy bitch. You're just glad the law was able to pry her
bloody talons from your back. It was idyllic, wonderful at first. You,
a pilot and later a war hero, and her, a brilliant engineer with the
second highest ranking position in Her Majesty's Engineering
Corps. Then things fell apart. You decided to design a revolutionary
fleet of airships for the good of the British Empire. Excitedly, the
two of you talked about designs and features for weeks, until you came
up with what was later to become the {\it HMS Dauntless}, first of the
new D-class of the Her Majesty's Aerial Navy. Of course, the {\it
Dauntless} is a luxury ship, not a military one, but the underlying
technology is still the same. But claiming the designs for the ship
was not \cCurie{}'s greatest offense. That is reserved for her
treatment of Mary. You love your daughter, and want her to grow up to
be a respectable young lady. But your ex-wife had other ideas. She was
a part of some "feminist movement", which as far as you can tell is an
excuse for women to act like rude men. She wanted to make Mary like
some sort of free spirited street woman, like some common whore. You
can't fully comprehend it, even. She always tried to get her to wear
boys' clothes and play violent games and do other things not suitable
for decent young ladies. When you married \cCurie{}, you had no idea
you were actually sharing wedding rings with the spawn of Lucifer. You
wanted her to cook dinner, and teach your lovely daughter how to be a
decent lady. But she fell deeper into the bizarre - she wanted to have
all sorts of disreuptable deviants in your house, and she even took
Mary to a suffragette demonstration!

Living became unbearable. You became morose, and more reserved, and
took to the bottle. Heavily. How could you bring up such faults in
open conversation? If she didn't know her mistakes, you certainly
weren't going to tell her. You two argued constantly, and her
insistence that she dreamed up the designs to the ship began to grate
on your ever-thinning nerves. One day you came home to find her things
missing and a terse angrily worded note. Mary was four at the time,
and you hope she doesn't remember her terrible mother. You ransacked
London looking for yourr daughter, and when you couldn't find her,
resorted to the courts. You sought a divorce. Hell, the Anglican
Church itself is founded on divorce. A bitter custody battle ensued,
over your daughter and your designs. Thank heaven you had Lord
Blackwell to stand with you in court and your brother help you keep
your sanity. \cCurie{} raged and lied and called you names
unmentionable in a polite setting. But the law prevailed. Mary was
yours to raise, and so was the {\it Dauntless}. You daresay you've
done a splendid job with both. 

You're not really sure what \cCurie{} has done in the interim, but you
heard about her recent appointment to the position of President of Her
Majesty's Engineering Corps, much to your surprise. It has been almost
fifteen years, though, and the men in charge now never knew the harpy
in her heyday. Not that Mary should know any of this. Last time she
saw her mother, \cCurie{} kidnapped her and took her to France. You
were insane with worry. Thankfully \cBoddy{} stood by you and went
with you to France to track them down. After three months she was
found by soem locals you had hired. The British courts sent her to
prison and banned her from contacting Mary as long as she remained a
minor. Mary has been told that her mother passed away, and seems to
intuitively know not to ask questions, but you can't help but wonder
if she ever thinks about her mother. What a horrible role model she
would be. Better off dead in the child's mind, than around to corrupt
her. But, like you said, Mary has been blossoming nicely. You hired a
new tutor for her a few weeks ago, to continue her voice lessons. Mary
sings like an angel, and she's only getting better. You hope this
lady, \cWhore{\intro}, will teach her how to be a proper lady. You'll
be watching to make sure. In fact, Mary is beginning to get
suitors. This would be exciting if they didn't seem so
Goddamn... lewd. The culture of this country has fallen, you're sure
of that, since you were a young man. When you courted \cCurie{} -
curse the day you ever decided upon that track! - you did all a
gentlemen aught to have done. You brought her flowers, called upon her
to join you and your family at operas and dinners, asked her parents
permission to marry her, and in general conducted yourself in a way
that made your heritage, education and bloodline clear to all. In
fact, you fear Mary has an eye for \cCid{}, your foul-mouthed head
engineer. That's not right at all. \cCid{} is a fine strong man who
knows the ship better than you do, but he's from a lower class than
what is fit for Mary. He could never do. It's times like this you
regret that Lord Blackwell didn't have a son.

You felt so honored when the British government decided to publicize
the maiden voyage of your ship, although you're sure your war buddy
Lord Blackwell had a hand in this. He's a politician, and a powerful
one, in the House of Lords. Practically the de facto leader of the
Conservative Party. You've been proudly voting the Conservative ticket
for two decades now. Lord Major, the prominent leader of the Labour
Party, will also be there. What shocked you, though, was that your
ex-wife, in her position as President of such an influential and
relevant group, decided to come herself. You haven't seen her in
almost fourteen years, and will at least try to be civil, even though
you hear she has been publicly speaking ill of the ship. The full
passenger list is in your pocket now, and you keep thumbing through
it. Your brother Reginald happens to be minister to Lord Major's
family, and is coming, too. He's a fine man of God, and though he's
been travelling all over the world recently, you're glad to have him
back. He looks different, though, as of late.  You wouldn't say
sickly, but something has changed in his demeanor. Perhaps he saw
things in the savage lands across the Ocean that civilized men were
not supposed to see. Perhaps his heart is heavy from some unspoken
burden. You've been meaning to speak with him, and maybe you can find
some time off to talk with him. Nonetheless, you're ecstatic to have
him on board, and to have had him staying with you lately. He sees
Mary so rarely nowadays, and you're sure there is no better influence
on a young woman than a caring Anglican priest. He always took care of
Mary when she was younger and you had to travel away from home.

But this should be a fun flight. You have an excellent list of
distinguished passengers, and a fine crew. Really, the only thing you
need to worry about it is running the Dedication in the middle of
the flight. The ship is to be dedicated to the glory of England and the Queen.
And while you're sure Cornelius will give a wonderful
speech, you still haven't really thought of an introduction. You're
sure Lady Major's display of the Neptune's Tear, and your brother's
Convocation will go off splendidly. Oh, about that. Lady Major's security detail locked the Tear in a hard to get into box and given it to her. Half of the locks can be opened by you, and the other half by her. Sort of a dual security system. You're not entirely sure why - it's not like there are thieves on board. Besides, you're really much more
interested in Mary's singing than anything else. She has the voice of
an angel, you tell anyone who will stand still long enough to hear. A
voice somewhat like Elizabeth's, but you don't dwell on that.  Your
ex-wife had some strange, ``liberated'' way of singing, and you
wouldn't want Mary to get any ideas. The current music tutor seems to
be fine, though you're tone deaf and can't really tell. She'd better
be fine. You're paying a pretty amount of pence for her.

{\it Oh.} Your heart grows weak again, and you need to sit down. Back in
the Steam War - there was a time when your ship was shot down by enemy
fire. Your parachute jammed, and you landed on the coast of France,
the twisted jagged metal exploding all around you and impaling your
broken body. When you awoke in a military hospital, you learned that
it was Lord Blackwell who fought off a half dozen French airships, landed
next to you, defeated a few land-based forces with his survival
hatchet, clawed and dragged you out of that melted ship, and flew
back to Britain just in time to save your life. Your old war wounds
overcome you sometimes. You used to take drugs, opium in particular,
to dull the numbing pain in your bones while young. You remember the
months after the war filled with that unfeeling everpresent black
haze, one which it took God to pull you out of, and marry your wife,
and raise your daughter. But you're not young anymore, and some of the
old pains have been returning more and more frequently. But this is
just a four-hour journey to Paris. Surely you'll be okay in the
meanwhile. Old soldiers never die, Lord Blackwell told you once. They just
fade away{\ldots}

%%%%%
%% The itemz environment is a list environment similar to itemize.
%% The typesetting is very tight, and matches that used by the lists
%% at the end of character sheets.  It takes an optional argument that
%% acts as a title for the list.  The enum environment is a similar
%% variation of the enumerate environment, and the desc environment is
%% similar to description.
\begin{itemz}[Goals]
  \item Ensure that the maiden voyage of the {\it HMS Dauntless} is a peaceful, safe success.
  \item Preside over the Dedication, and make sure those that are a part of it are ready.
  \item Compose a speech for the Dedication.
\end{itemz}

\begin{itemz}[Notes]
  \item You are the captain of the ship. Act like it.
  \item The Dedication is scheduled to take place two and a half hours after takeoff.
  \item No suitor of Mary's who can't prove to you that they are a gentleman can ever have your blessing.
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cThief{}} Your daughter, whom you love more than life and flight itself. Well, maybe just life. She has just turned eighteen years old.
  \contact{\cBoddy{}} The two of you go a long way back.
  \contact{\cCid{}} A crude, tempestuous young man, but a loyal worker, and one of the best engineers you know.
  \contact{\cWhore{}} Mary's music and literature teacher.
  \contact{\cCurie{}} Your estranged wife. You don't want her influencing your daughter.
  \contact{\cVicar{}} Your brother, a good upstanding man.
  \contact{\cRobot{}} A small boy who shovels coal in the back your the ship.
\end{contacts}

%%%%%
%% \starttag{<tag>} <elements> \endtag 
%% Valid <tag> values are blues, greens, abils, combat, mems, items,
%% whites, notebooks, cash, signs, ids.  These each correspond to a
%% type of macro defined in Lists/.
%%
%% By using \starttag, you can give this character <elements> of the
%% type corresponding to <tag>.
%%
%% Multiple uses of the same <tag> will simply add together.

\starttag{mems}
  \memfold{Open at game start.}{A series of explosions rock the airship! You are thrown to your
 knees, clutching at your chest. Your old war wounds are acting up again, more seriously than they
 have in decades. In a second of desperate agony, your body cries out for the numbing effect of opium{\ldots} {\em Open your} {\bf X Packet}.}
  \memfold{If you see {\bf item \# 35-C} or {\bf item \# 152}.}{{\em Now how did that go again?} Oh,

right. {\em 32-4-22}. This is the combination that opens some of the locks on the {\em HMS 

Dauntless}. You may now freely {\bf item \# 35-C} and {\bf item \# 152}. You can tell the combo to 

other people. If you do this, tell them to open their {\bf L Packet}.}

\endtag

\end{document}
