\documentclass[char]{guildcamp1}
\begin{document}
\name{\cPassive{}}

Your name is \cPassive{\they}. You are a prominent scholar of a galaxy-spanning species that calls themselves the \emph{Xenids}. Your species started off as an eight-legged species that relied upon bulky claws for fine-scale manipulation. Over the centuries your species shed its apprehension to large-scale genetic engineering and adoped a multisexual, bipedial, two-armed form that you copied from several other successful species. Your civilization is very powerful, but is currently at war with a smaller but more advanced galaxy-spanning civilization called the \emph{Illithids}. The latest reports suggest you are losing the war and some of the planets on the border stars of your civilization are being conquered. This doesn't concern you too much; you are not a soldier and have little interest in the war, and the border stars are really just small colonies that are easily evacuated. You were born on the Xenid home world which is quite far away from the war front and not likely to be threatened anytime soon. Your passion is learning and studying new things from outside the Xenid civilization and bringing them back home.

The majority of the Xenids, athough not strictly xenophobic, prefer to stay on Xenid-controlled planets and do not interact with other species. Depending on who you ask, you are either blessed or cursed with a personality that has no trouble interacting with foreign species. This gives you a clear advantage in the Xenid academic social circles --- while others tend to sit around analzying and debating data collected by others, you actively reach out and gather new knowledge. Towards this end you joined \emph{Contact}, the exploratory and scouting branch of the Xenid hierarchy. Contact's primary goal is to gather data on new species: ``How technologically advanced are they?''; ``How does their government work?''; ``Are they a military threat?''; ``Are they a potential ally?'' There are hundreds of billions of stars in the Milky Way and only some support life, so there are always plenty of uncharted stars out there.

Your current contact assignment is to investigate an unknown energy signature detected at a planetless blue dwarf star. You are in a two-person vessel, and your partner is \cAlien{\they}. She is a soldier from one of the border star systems. Her home planet is currently under siege and has possibly already fallen. In your previous encounters with her, you have found her to be very focused on finding allies or military technology from other civilizations to help with your war against the Illithids, to the point where she is willing to violate some of the conventions designed to prevent large-scale conflict resulting from a first-contact gone sour.

On your way to the blue dwarf, your sensors picked up what you believed to be an unknown ship traveling at a very high fraction of the speed of light. You and \cAlien{\they} debated for some time what action to take. You argued that the unknown ship was not emitting any signals and was clearly not interested in being discovered, so might destroy your small scout ship to maintain its stealth profile. \cAlien{\they} argued that the potential benefits outweighted the risks; a cursory material analysis suggests that whoever built this ship is technologically comparable to, and might even surpass, the \emph{Illithids}. While you were busy debating this, the ship's main power supply seemed to falter and die, and it started emitting a string of sequential binary-coded prime numbers. Your curiosity now peaked and taking the sequence of primes to be a distress signal of sorts, you both decided to get closer and investigate the ship.

The ship consists of four main components: a solar array, a battery system, an ion engine, and a massive computer. The solar array and battery system are superior to anything your civilization can manufacture, with an almost 100\% energy conversion ratio and almost no passive battery loss, while the ion engine is mediocre at best. The computer however is the part that fascinates you the most, as it clearly surpasses both Xenid and Illithid design. It consists of a wide array of subatmoically packed memory cells tightly intermixed with equally small-scale processing units. There is no atmosphere on the ship, but there are three robot bodies wirelessly hooked up to the computer system.

The odd powering down of the ship's system you witnessed recently seems to have caused all but a very small part of the computer system. What is left.

High-density data source.

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cActive{}} 
\end{contacts}


\end{document}
