\documentclass[char]{guildcamp1}
\begin{document}
\name{\cRival{}}


Success is sweet.  You are a world-known expert in brain computer interaction.  You made millions of dollars founding your own company.  

Your professional career took off in graduate school when you discovered a way of measuring the activity of individual neurons in a human brain.  A few years earlier, physicists had developed superconducting magnets that were only one centimeter in diameter, and you realized that by creating a cylindrical array of these magnets you could focus them on individual neurons.  After a few years of work you created a device that could detect a person's surface thoughts. With this person could think ``I want to send an email to Bob that says the following: . . .,'' and would it detect this and take the required action automatically.  After graduate school, you founded a start-up with this technology and earned hundreds of  millions dollars.  You love the power this money gives you.  You often carry a million dollars of stocks around with you, to remind yourself of your wealth and to trade if you find someone who has something you really want.

You have continued working on your brain-computer interface in a huge lab at your company, and you have reached a new milestone.  You can now build a device that can scan all the neurons and all the connections between them in a living human brain.  You have brought the parts to build this machine for a conference tomorrow, and you're sure your work deserves the International Medal of Science, the highest honor a scientist in any field can receive.  This is it, a chance to prove to everyone just how successful you are.

The only obstacle between you and the award is your longtime rival, Dr.~\cScientist{\intro}.  Your rivalry with \cScientist{} began in high school at the International Science Fair.  %Note: this is intentionally different from scientist's account.  They both remember the other doing the first bad thing.
You were set to win, but the night before the competition \cScientist{} broke into your hotel room and sabotaged your project, causing you to forfeit.  You didn't have any evidence, but you know it was \cScientist{\them}.  You got back at \cScientist{\them} at the International Computing Olympiad, when you sabotaged \cScientist{\their} computer, forcing \cScientist{\them} to forfeit while you took first place.  You and \cScientist{} have gone back and forth attacking each other over the years.  For example, as an undergraduate when you both applied to the Journal of the National Academy of Science you hacked into the journal's server and changed your submission to an acceptance and \cScientist{\their} submission to a rejection. This was the one prank you pulled that someone managed to collect evidence of.  Your old friend \cBride{} found out, but luckily she wouldn't betray you.  You would hate for any of your illegal activities to get out and damage your reputation.

Today your plan to knock \cScientist{} out of the running for the International Medal is simple.  With some hacking you managed to obtain a copy of the paper \cScientist{\they} is submitting tomorrow.  You have created a copy of this paper which looks similar but commits clear plagiarism of another scientist's work.  You'll get hold of \cScientist{\their} folder which contains \cScientist{\their} paper and swap the real and faked paper.  You can't wait to see the press when they find out tomorrow.

You have thought about what to do next with your brain-computer interface technology, and realize it would be very powerful if combined with an advanced artificial intelligence.  Perhaps you could scan a human brain and then run a simulation of it inside a computer.  This would require a very advanced artificial intelligence, but your rival \cScientist{} has been working on just such a technology.  Of course \cScientist{\they} would never give it to you if you asked, and \cScientist{\their} security is too good for you to steal it directly.  However, \cScientist{\they} has been working with the military, and you happen to know the military security at this hotel is weak.  There is a high security door at this hotel, and you plan to find a way inside it and take the autonomous drone technology behind it.  You can't wait to reverse engineer the drone back at your company lab next week and see how it works.

\begin{itemz}[Goals]
\item Steal the autonomous drone prototype from behind the high
  security door.
\item Hang onto your stocks or trade them for something sufficiently valuable.
\item Frame \cScientist{} for plagiarism
\end{itemz}

%TODO make sure relevant items and mechanic exist for plagiarism plot.  Should the foler/paper be physrepd?
% TODO Rival has an item of stocks
% TODO make sure Rival has drugs/meth
% TODO: get widget or give widget to Scientist
% TODO: make science more sketchy


%Your pronoun is \cRival{\they}.

%%%%%
%% List contacts, using \contact{<char macro>}
%\begin{contacts}
%  \contact{} 
%\end{contacts}


\end{document}
