\documentclass[blue]{guildcamp1}
\begin{document}
\name{\bVirtuism{}}

As a practitioner of Virtuism, you are familiar with its basic tennants. They are listed below, as they appear in a contemporary work by \cPastor{\MYname{}}.

\begin{itemize}
  \item \cGod{\MYname{}} is great, and can do many things for you. He will do nothing for you however, if you do not strive to help yourself, and each other, first. When you have done all you can, \cGod{\MYname{}} will do the rest.
  
  \item \cGod{\MYname{}} has given us all the power to affect change. We should never squander that power. 
  
  \item All are expected to look for the signs of the doomsday, and be prepared to do their part to prevent it. 
  
  \item Geneosity is crucial to the maintanance of our community of devotees. We must not fixate on worldly possessions, or selfish uses of our time. However, one must never look to the needs of others without first meeting his or her own needs.
  
  \item Technology is the enemy of Virtuism. Atheists worship technology and seek to subvert our devotion to \cGod{\MYname{}} for their own, selfish ends. No devout follower of Virtuism should willing to participate in, or cooperate with, any ritual that involves the usurping of items and symbols of great value to Virtuism such as those used in initiation, rites of passage, weddings or funerals.
  
  \item The nuclear family is incredibly important, particulaly for the raising of children. Potential life partners should embrace Virtuism as ardently as you do. Further, anyone who allows a child out of wedlock should be expelled from our ranks and be prevented from participating in the ceremonies of Virtuism.
  
  \item Above all, Virtuism strives for clarity of self. Reflect often upon yourself to help you to understand \cGod{\MYname{}}'s plan for you. Never doubt yourself, or what you know to be true through this self reflection.
\end{itemize}


\end{document}