\documentclass[blue]{guildcamp1}
\begin{document}
\name{\bVirtuism{}}

As a practitioner of Virtuism, you are familiar with its basic tenants. They are listed below, as they appear in a contemporary work by \cPastor{\MYname{}}.

\begin{itemize}
  \item \cGod{\MYname{}} is great, and can do many things for you. He will do nothing for you however, if you do not strive to help yourself first. When you have done all you can, \cGod{\MYname{}} will do the rest.
  
  \item \cGod{\MYname{}} has given us all the power to affect change. We should never squander that power. 
  
  \item All are expected to look for the signs of the doomsday, and be prepared to do their part to prevent it. 
  
  \item Generosity is crucial to the maintenance of our community of devotees. We must not fixate on worldly possessions, or selfish uses of our time. However, one must never look to the needs of others without first meeting his or her own needs.
  
  \item Worshippers of technology are the enemy of \cGod{\MYname{}}. Atheists worship technology and seek to subvert our devotion to \cGod{\MYname{}} for their own, selfish ends. Use technology if you must, but do not bow to it, and do not allow it to control you.
  
  \item The nuclear family is incredibly important, particularly for the raising of children. You should not marry anyone who has not embraced Virtuism. It is sinful to have intimate relations outside of marriage, and even more so to raise children outside of the holy bond of matrimony
  
  \item Above all, Virtuism strives for clarity of self. Reflect often upon yourself to help you to understand \cGod{\MYname{}}'s plan for you. Never doubt yourself, or what you know to be true through this self reflection.
\end{itemize}


\end{document}