\documentclass[white]{guildcamp1}
\begin{document}
\name{\wUtopianLetter{}}

\emph{(A mysterious letter you found in your pocket)}

Dear reader,

You have no idea who I am, and I do not really know you you are. Through a variety of methods, I have reason to believe you may be sympathetic to my cause. You likely do not have time to waste, so I am going to bring you up to speed very quickly. I apologize in advance for my bluntness.

The world you are in is not real. We abandoned our home planet, called Earth, a long, long time ago. You are just a disembodied mind in a giant simulation that is likely drifting through space.

You might be wondering why we made a simulation that included such troubles as poverty, starvation, disease, sickness, and cancer. Indeed many of us, myself included, fought quite strongly for the construction of a simulation that contained none of these. We called ourselves the Utopians, but ultimately our voices were drowned out and the flawed simulation you live in was created instead.

But if you are reading this letter, that means circumstances have likely changed. I don't know exactly what happened, but there is now a chance to set the world right. The Utopians secretly constructed a sophisticated program that will rewrite the world you live in according to our ideals. We have designed it such that all the minds encoded in the system will remain; the program will just remove all the problems that are prominent in the real world but totally unnecessary in a virtual one. If there is any damage to the simulation --- and if you are reading this message, there almost certainly is --- the program will also repair that.

You might ask, where do you come into play. You see, this program is now encoded in a physical object somewhere in your world. Unfortunately due to the nature of the simulation I don't know exactly what or where this object is, but it should materialize near you. If you can take this object outside of the simulation, you will wake up in a ship and the object will transfer with you. You may think you know nothing about computers, but what you have to do is very simple --- simply insert the object into the slot prepared for it. The program will take care of the rest.

I'm afraid I can offer you fairly little advice on actually getting out of the simulation. I am writing this letter in what to you will seem the distant, distant past and I know nothing of your world. But it is likely that there are forces at work around you searching for a way out. Follow them closely but do not reveal your hand too soon --- if the wrong hands discover the Utopian program, they will certainly seek to destroy it.



Good luck,
A friend

\end{document}
