%%%%%
%%
%% Notebooks live in this directory.  There are two kinds: in-game
%% notebooks (like classic research notebooks) and out-of-game
%% notebooks (also known as green notebooks).  Both kinds are defined
%% in Lists/notebook-LIST.tex.  In-game notebooks, defined as Notebook
%% macros, get assigned in \MYitems.  Out-of-game notebooks, defined
%% as GreenNotebook macros, get assigned in \MYgreens.
%%
%% This file doubles as a latex'able example out-of-game notebook.
%% README.tex, also in this directory, doubles as an example in-game
%% notebook.
%%
%% Notebook and GreenNotebook macros each have a file that lives here.
%% The argument to \startnotebook{...}  probably should be the macro
%% for the given notebook.  However, you can also just use
%% \startnotebook{Some Text} if you want.
%%
%% Note that every \startnotebook command needs a matching
%% \endnotebook command.  Also note that no ownership information
%% appears on the notebook.
%%
%%
%% If you want to use notebooks for memory packets, see related macros
%% in Lists/mem-LIST.tex (and in Charsheets/README.tex).  If you want
%% more programmatic control over the structure/linkage of notebooks,
%% like for a computer security mechanic, see LabelCover and LabelPage
%% in Lists/sign-LIST.tex.
%%
%%%%%

\documentclass[greennotebook]{guildcamp1} %% [notebook] or [greennotebook]
\begin{document}

\startnotebook{\nVirus{}}



%% The argument to \begin{page}{...} is a reference string.  You use
%% \nbref{...} in page text to refer to a given page.  These
%% references will be typeset as numbers, based on the order of the
%% pages.
\begin{page}{first}

This notebook is not transferable. If your $\omega$-score drops to 8, you may turn to the next page.

\end{page}

\begin{page}{second}

Oh dear, you feel a little odd. The world seems to be moving faster than you are, in leaps and twitches.

You can only walk heel-to-toe and cannot run for five minutes.

Every time your $\omega$-score drops again, you must walk heel-to-toe for another five minutes.

If your $\omega$-score drops to 3, you may turn to the next page.

\end{page}


\begin{page}{third}

How frustrating! You can think clearly, but every word coming out of your mouth seems to be garbled. Is your tongue not working?

You can only communicate in gibberish for five minutes. Feel free to gesture. You also have to walk heel-to-toe for five minutes.

Every time your $\omega$-score drops, you must talk in gibberish for another five minutes, as well as walking heel-to-toe for five minutes.

If your $\omega$-score drops to 1, turn to the next page.

\end{page}



\begin{page}{fourth}

In addition to talking gibberish and walking heel-to-toe, open your $\omega$ mempack.

If your $\omega$-score drops to 0,  turn to the next page.

\end{page}



\begin{page}{fifth}

Oh no, this isn't supposed to happen. You hear a ringing, screeching drone, like a phone dial, and everything goes dark.

You are now in permanent coma, and are effectively dead.

\end{page}



\endnotebook

\end{document}
