\documentclass[green]{guildcamp1}
\begin{document}
\name{\gPrepareWedding{}}

As a practitioner of Virtuism, with a role to play in this most sacred ceremony, you have explicit knowledge of how to prepare for the Wedding ceremony. The ceremony requires actions on the part of the {\bf bride}, the {\bf groom}, the {\bf pastor}, and one {\bf witness}. You are highly encouraged to recruit as many witnesses as possible for the ceremony, although only one is necessary.

{\bf Keep in mind that Virtuism does not allow weddings to occur after dark.} Sundown is at 11:00 pm tonight.

{\bf Before preparations for the ceremony can begin, everyone interested in participating, including witnesses, should attend a prayer circle 3.5 hours before dark} (which translates to 30 minutes after game start). {\bf A prayer circle is simply everyone joining hands for 30 seconds.} 

If you wish to fulfill the conditions of being the {\bf Bride} or the {\bf Groom} you must complete the following tasks, in any order you choose:
\begin{itemize}
  \item Collect a {\bf flower} from a {\bf pot}. Make sure to bring it to the ceremony!
  \item Spend 3 minutes in conversation with someone about the ceremony. {\it Role play accordingly.}
  \item Spend 5 minutes alone in contemplation of your vows. {\it Simply choose not to interact with anything or anyone since you are contemplating your vows. You may do this anywhere, as long as no one is within 2 ZoC. If someone enters this range you may warn the person and if they immediately retreat, you may continue. Otherwise, you must start over.}
  \item Spend 2 minutes in your {\bf room}, getting ready. {\it Stand with both hands on the sign for your room for your room for 2 minutes.}
  \item If you are the {\bf Bride}, get somebody to brush your hair.
  \item If you are the {\bf Groom}, get somebody to shine your shoes.
  \item Practice dancing with the bride or groom for at least 5 minutes. {\it Role play accordingly.}
\end{itemize}

If you wish to fulfill the conditions of being the {\bf Pastor} you must complete the following tasks, in any order you choose:
\begin{itemize}
  \item Collect a {\bf flower} from a {\bf pot}. Make sure to bring it to the ceremony!
  \item Spend 2 minutes in conversation with one non-believer, explaining the importance of the wedding ceremony.
  \item Bring enough {\bf glasses} of wine (3 plus any witnesses. Don’t hesitate to bring extras) from the {\bf Bar} to the {\bf Ballroom}. {\it Glasses have a bulkiness of 1 hand. You may therefore carry up to 2 at a time, if you are carrying nothing else. Since they are fragile, you must walk heel to toe whenever you are carrying at least one wine glass. Don’t spill!}
  \item Spend 3 minutes preparing your speech which you will deliver at the beginning of the ceremony.
\end{itemize}

If you wish to fulfill the conditions of being a {\bf Witness} you must complete the following task {\it (note: non-believers can act as witnesses if they have spoken to the pastor):}
\begin{itemize}
  \item Collect a {\bf flower} from a {\bf pot}. Make sure to bring it to the ceremony!
\end{itemize}

%% do I need to name each list?

\end{document}