\documentclass[char]{guildcamp1}
\begin{document}

\name{\cBride{}}
\bigquote{``Her power has been made to derive from her sexuality. It has always been preferable to attribute a woman's success to her beauty rather than to her brains, to reduce her to the sum of her sex life.''}{--Stacy Schiff}

You look out of the window, only to find{\ldots} Nothing. There is nothing there. No sky, no clouds, no beautifully manicured garden. Not even the other tower of the Hotel Virtuoso. You stare for a heartbeat, then dive for your Testament. Flipping frantically through the pages, you find {\em The Prophesy}. Your heart beats faster and faster as you read the familiar words again. There is no mistaking that the time talked about in the prophesy is now. You try to catch your breath as you spin around and stare at the wedding dress hanging in your closet. It's you. You are the one talked about in the prophesy. Destined to save the world.

A bitter laughter wells up inside you. How could you be destined to save the world? You don't feel like anything special; your father made sure of that when he left you and your mother. You were just eight years old when he absconded with your mother's fortune. Your mother was heartbroken, and had gotten into some hard core drugs. She died from an overdose when you were just 14.

You snap out of your painful reminiscing. You are not a sob story. You are strong. Independent. Beautiful. Oh yes, you are so beautiful. After your mother abandoned you, just like your father before her, you turned to Virtuism for comfort. What you found there brought you great clarity. You embraced the tenets wholeheartedly, particularly the ones about being self reliant and true to yourself.

In college you met \cRival{}, with whom you became fast friends. \cRival{They} was a nice \cRival{kid}, though not very religious. \cRival{They} didn't seem to understand Virtuism the way you did. It explained so much of the world to you. \cRival{Them} refusal to follow Virtuism closely led \cRival{} astray a couple of times and you had to rescue \cRival{them}. In particular, \cRival{they} got \cRival{themself} mixed up with a \cRivalEx[{kid} who echewed Virtuism in all it's manifestations. \cRivalEx{They} made your friend misserable. When \cRivalEx{they} started hitting on you as well, you saw a golden opportunity to teach \cRivalEx{them} a lesson. A few dates and a dramatic break-up in front of half of the sophomore class left \cRivalEx{their} world shattered, and you drunk with power.

After that, it was like a drug. Leading men on, taking whatever you could from them, and leaving them broken--it was fun. Your conscience never bothered you. The men you targeted deserved to be exploited. You ruined reputations, extorted money, and climbed the social ladder yourself. Through it all, you justified it as 


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cGroomA{}} 
\end{contacts}


\end{document}

