\documentclass[char]{guildcamp1}
\begin{document}
\name{\cKid{}}

Your name is \cKid{}. You are seven years old. Your mom is \cScientist{}. She's a pretty great mom, even though she's always working and sometimes doesn't have enough time to spend with you when you want her to. 

You were raised by your mom and a nanny, and you never met your dad. You've grown up seeing other kids with their dads and seeing people playing with their dads on TV, and you've always wanted to have a dad too. So when your mom told you that she's going to take you to meet your dad, you got really excited! But when the two of you got to the hotel where she said your dad would be, it turns out that your dad is getting married to SOMEONE ELSE! This is horrible. This is not what you were thinking at all. You thought that meeting your dad meant that he'd get back together with your mom and be like a real dad to you, like the dads you've seen on TV. So you want to try to make that happen. 

Your mom has been worried about something lately, but you don't know what it is. She gets sad and cries at night. You wish she wouldn't because it's scary.

You do have one special talent, though. It's super special and also a big secret because people yell at you when they find out. You are really small and sneaky, and you can steal anything. 

\begin{itemz}[Goals]
  \item Keep your teddy bear safe.
  \item Play with your dad!
  \item If you can steal the wedding ring away from your dad's new fiance, maybe he won't marry her and get back with your mom and you'll have a real dad!
\end{itemz}


%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{\cScientist{}} Your mom. You love her so much!
  \contact{\cGroomA{\MYname}} Your dad. You've never met him but you love him!
\end{contacts}


\end{document}
