\documentclass[char]{guildcamp1}
\begin{document}
\name{\cScientist{}}

Thirty days.  That is the expected length of your life.  You have an inoperable brain tumor, and there's nothing you can do to save yourself.  You've researched every case recorded on any database of medical records, even the databases that required some hacking to access, and you haven't found word of a cure anywhere.  All you've found is cold, hopeless statistics.  The standard deviation of the length of your life is twenty days.  You had better make the best of the days you have.

First, your professional life: you are a world-known artificial intelligence researcher. You specialize in creating simulated worlds that are incomparably more realistic than any previous game or simulation.  Twenty years ago, a breakthrough in custom circuit design allowed researchers to start making neural networks with a trillion simulated neurons, ten times the number there are in the human brain.  Of course this terrific hardware is useless without the machine learning software to run on it, and that is were you came in.  You received your PhD  16 years ago for creating a revolutionary new approach to machine learning on this custom hardware.  Ever since then you have been working in the largest research lab in the world improving your ideas and making them a reality.

One of the goals of your life has been to win the Turing Award, ``the Nobel Prize of computing,'' for your work.  You had thought that you 20 more years to win this award, but with you brain tumor you realize you will either win it this year or you will never experience that achievement.  The two serious contenders for the award are Dr.~\cRival{\intro{}}, your nemesis.  

You and \cRival{} became enemies when you were both in high school.  During your senior year of high school at the International Computing Olympiad, \cRival{} sabotaged your computer, so you placed last while he placed first.  You had your revenge as an undergraduate when both of you applied to the same prestigious journal and you sabotaged \cRival{}'s computer two hours before the deadline and caused him to miss it.  Similar pranks and worse have occurred throughout your career.  The latest attack was six months ago when \cRival{} hacked into your doctor's computer, learned of your disease, and forwarded the details to several blogging sites.  You hadn't told anyone, even your parents, because you didn't want their sympathy.  You have learned to back up your work, encrypted, on several different servers, to always carry an extra laptop in case the first is hacked into, and to never turn you back on \cRival{} when you are at conferences together. 
You have done some contracting for the military in the past.  Using your artificial brain, they have created drones that can follow high level commands like ``Find and capture a person who looks like this picture and lives in that village.''  You were reluctant to let your beautiful ideas be used for war, but you were assured the drones would only be used to capture known terrorists who had killed Americans.  A prototype of your drone is actually going to be demonstrated tomorrow at this hotel and is being stored in a high security room.  When you were doing your routine spying on \cRival{}, you overheard that he is planning to steal your prototype.  To secure your prototype and show the world once and for all what a scumbag Rival is, you have a plan to install a camera in the room where your prototype is stored.  You hope to catch Rival in the act of stealing it. See sheet TODO.

 Your personal life has usually come second to your professional life, but you have had one romantic relationship.  TODO(check Kid's age) years ago, you fell in love with \cGroomA{\intro{}} when you met him through your military consulting work.  You are not usually sentimental, but your research had been going poorly at the time and your hormones took control. For six months you spent almost all your waking time (and all your sleeping time) with \cGroomA{},% letting your research slip into neglect.  %Then you have a negative performance review at work, the only negative review you have ever had.  You also realized that you weren't really enjoying your time with \cGroomA{}.  Your true passion was research. You left \cGroomA{}, and haven't strayed from your research since.  
even spending less time on your precious research to spend more time with him.  You became pregnant and were planning to raise a child with him.  Then you discovered his betrayal.  He was selling your drones to authoritarian dictators to help them track down dissenters.  How could be molest your work like that, using elegant ideas for evil?  You left him the next day.  You mentioned the child in your womb, but you decided you didn't want anything more from this man.  TODO(maybe you were too hard on him? change of mind?)
You would enjoy one last close encounter with \cGroomA{}, and you hope you'll get a chance to spend some time with him alone this evening.

Your relationship with \cGroomA{} did produce one awesome result, your child \cKid{}. You hadn't planned to have children, but you have loved \cKid{} since the first moment you laid eyes on \cKid{\they}.  You're sorry to say that \cKid{\they} has probably spent more time with your nanny than with you, but the times you have shared have been truly special.  It is essential that \cKid{\they} has a good home after you pass away, and you have decided the groom is the best choice.  You've been telling \cKid{} about his wonderful father for the last month, and you're sure \cGroomA{} will melt and accept \cKid{} when he sees who excited \cKid{\they} is to be with \cKid{\their} father.

TODO more writing?

Religiously, you have always been a strong atheist.  Ever since you learned of your tumor you have vaguely wished there were a life after death, or some supernatural way to cheat an untimely death.  But you value truth far too highly to entertain wishful thinking.  The cold, hard truth is that this universe and this life are all you have.



\begin{itemz}[Goals]
  \item Convince \cGroomA{} to take care of \cKid{} once you're gone
  \item Spend some time alone with \cGroomA{}
  \item Catch \cRival{} stealing military secrets
  \item Survive if you can
\end{itemz}

%%%%%
%% List contacts, using \contact{<char macro>}
\begin{contacts}
  \contact{} 
\end{contacts}


\end{document}
